Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-22 Grassmannian_cells.tex
eliminated some warnings and overfull hboxes

\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
\usepackage{tikz}
\usepackage{pgflibraryarrows}
\usepackage{pgflibrarysnakes}
\usetikzlibrary{fit}
\usepackage[margin=1in,marginparwidth=0.8in, marginparsep=0.1in]{geometry}
\usepackage{extarrows}
\usepackage{verbatim}
\input xy
\xyoption{all}

@@

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfJ}{\mathbf{J}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\Att}{\operatorname{Att}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
\newcommand{\ses}[3]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
\newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\newcommand{\supp}{\operatorname{supp}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

As mentioned above, the Laurent polynomial expressions for cluster variables have been described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.
For rank two cluster algebras, the Laurent expressions of cluster variables can also be computed using a certain Dyck path combinatorics \cite{lee-li-zelevinsky}.
The confluence of these results gives rise to a combinatorial construction for the Euler characteristics and counting polynomials of certain quiver Grassmannians.
A consequence of our main result is a geometric explanation for these computations: we provide a one-to-one correspondence between the strong successor closed subsets and compatible pairs for an appropriate Dyck path which leads to a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians.

\sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}

\sayT{references need to be included}

-something about compatible pairs and combinatorial construction of cluster variables\\
-statement of our results\\
-something about torus actions and the universal cover\\
-something about cell decompositions of quiver Grassmannians\\
-acknowledgements?\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}
\label{sec:RepK(n)}

@@

\subsection{Lifting to $\widetilde{K(n)}$}
\label{Lifting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$GL_n$ Action on Arrows of $K(n)$}
The goal of this section is to prove Theorem~\ref{thm:truncpp} showing that quiver Grassmannians of truncated preprojectives $P_{m+1}^V$ are smooth and only depend on the dimension of the subspace $V\subsetneq H_m$.
We begin by observing that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{\alpha_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{\alpha_i})$ with $(g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{\alpha_j}=N_{\alpha_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$ and $1\le i\le n$, we have
  \[\theta_2\circ (g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{\alpha_j})=\sum\limits_{j=1}^n g_{ij}(N_{\alpha_j}\circ\theta_1)=(g.N)_{\alpha_i}\circ\theta_1\]
  so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}

@@

\subsection{$2$-Quivers}

@@

\item  For $m\geq 3$, recall that we have $\dim\Hom(P_{m-1},\tau P_m^{[k]})=\dim\Ext(P_m^{[k]},P_{m-1})$ by the Auslander-Reiten formula. This induces isomorphisms
\begin{align}
  \label{eq:homext} 
  \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}. \tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).
\end{align}
This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$. 
In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_m^{[k]}$. Finally note that there exists a short exact sequence
\[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
\end{enumerate}
\end{remark}

@@

\begin{tikzpicture}[scale=1.4]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

For $m\geq 3$, the truncated preprojective $\tau\tilde P_{m+1}^{[k]}\cong\tilde P_{m-1}^{[k]}$ can uniquely be found as a quotient of $\tilde P_{m,k}$. This can also be seen on the level of $2$-quivers, i.e. we find $\cQ_{m-1}^{[k]}$ as a subquiver of $\cQ_{m,k}$.  More precisely, this subquiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,k}$.  Now the $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$ of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ to $\mathcal Q_{m,k}$ by a $2$-arrow. Thereby, the $2$-arrow connects $\mathcal Q_{m+1}^{[k]}$ to the subquiver $\cQ_{m-1}^{[k]}$ in $\cQ_{m,k}$. This gives the following $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$:
\\

\begin{tikzpicture}
\draw (0,4) node (A1) {\footnotesize$\mathcal Q_{m-1,1}$}+(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,k}$} +(1.6,0) node (B1) {\footnotesize$\mathcal Q_{m-1,2}$}+(1.6,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$} +(3.2,0) node (B11) {\footnotesize$\dots$} +(4.6,0) node (D1) {\footnotesize$\mathcal Q_{m-1,n-1}$}  +(6.4,0) node (E1) {\footnotesize$\mathcal Q_{m-2,2}$} +(4.8,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}+(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}+(8.0,0) node (A1b) {\footnotesize$\dots$} +(9.6,0) node (B1b) {\footnotesize$\mathcal Q_{m-2,k+1}$}+(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[k]}$} +(11.2,0) node (B11b) {\footnotesize$\dots$} +(12.8,0) node (D1b) {\footnotesize$\mathcal Q_{m-2,n-1}$} +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$} +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$} ; 
\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
\draw[<-,red] (D1b)--(E1b) node[pos=.5,above] {};
\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {};
\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {};
\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {};
\draw[->,red] (Q41)--(E1) node[pos=.5,above] {};
\draw[->,red] (Q51)--(D1) node[pos=.5,above] {};
\draw[->,red] (Q61)--(B11) node[pos=.5,above] {};
\draw[->,red] (Q71)--(B1) node[pos=.5,above] {};
\draw[->,red] (Q81)--(A1) node[pos=.5,above] {};

@@

\node (PMK) [draw=black,fit={(Q2b) (B)}]{};
\draw[->,red,thick] (PMK)--(Q31);
\end{tikzpicture}
\\

\noindent 
%In order to keep the diagrams as simple as possible we did not insert the labels of the vertices. As every vertex  $q\in(\mathcal Q_m^{[k]})_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q_m^{[k]}$. 
 As already mentioned two different vertices of $\mathcal Q_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$. Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[k]})_0$ are defined by
$$\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G_{K(n)}\tbfe (\beta)\in\NN^{K(n)_0}$$
where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta\subset (\mathcal Q_m^{[k]})_0$.

@@

The following result is an immediate consequence of the combinatorial construction of rank 2 cluster variables \cite{lee-li-zelevinsky} and the categorification of these variables using representations of $K(n)$ \cite{cc,caldero-keller}.
\begin{theorem}\cite{lee-li-zelevinsky}
  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(\Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
\end{theorem}

Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(\Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.

>>>>

\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
\usepackage{tikz}
%\usepackage{pgflibraryarrows}
%\usepackage{pgflibrarysnakes}
\usetikzlibrary{fit}
\usepackage[margin=1in,marginparwidth=0.8in, marginparsep=0.1in]{geometry}
\usepackage{extarrows}
\usepackage{verbatim}
\input xy
\xyoption{all}

@@

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfJ}{\mathbf{J}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\Att}{\operatorname{Att}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
\newcommand{\ses}[3]{\xymatrix@C15pt{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
\newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\newcommand{\supp}{\operatorname{supp}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

As mentioned above, the Laurent polynomial expressions for cluster variables have been described using the representation theory of quivers \cite{cc,ck}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.
For rank two cluster algebras, the Laurent expressions of cluster variables can also be computed using a certain Dyck path combinatorics \cite{llz}.
The confluence of these results gives rise to a combinatorial construction for the Euler characteristics and counting polynomials of certain quiver Grassmannians.
A consequence of our main result is a geometric explanation for these computations: we provide a one-to-one correspondence between the strong successor closed subsets and compatible pairs for an appropriate Dyck path which leads to a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
\sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
-something about compatible pairs and combinatorial construction of cluster variables\\
-statement of our results\\
-something about torus actions and the universal cover\\
-something about cell decompositions of quiver Grassmannians\\
-acknowledgements?\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of Generalized Kronecker Quivers}
\label{sec:RepK(n)}

@@

\subsection{Lifting to \texorpdfstring{$\mathbf{\widetilde{K(n)}}$}{K(n)}}
\label{Lifting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\texorpdfstring{$\mathbf{GL_n}$}{Gln}-Action on Arrows of \texorpdfstring{$\mathbf{K(n)}$}{K(n)}}
The goal of this section is to prove Theorem~\ref{thm:truncpp} showing that quiver Grassmannians of truncated preprojectives $P_{m+1}^V$ are smooth and only depend on the dimension of the subspace $V\subsetneq H_m$.
We begin by observing that $GL_n(\CC)$ naturally acts on the vector space $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ spanned by the arrows of $K(n)$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on the path algebra $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{\alpha_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{\alpha_i})$ with $(g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}M_{\alpha_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{\alpha_j}=N_{\alpha_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$ and $1\le i\le n$, we have
  \[\theta_2\circ (g.M)_{\alpha_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{\alpha_j})=\sum\limits_{j=1}^n g_{ij}(N_{\alpha_j}\circ\theta_1)=(g.N)_{\alpha_i}\circ\theta_1\]
  so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}

@@

\subsection{2-Quivers}

@@

\item  For $m\geq 3$, recall that we have $\dim\Hom(P_{m-1},\tau P_m^{[k]})=\dim\Ext(P_m^{[k]},P_{m-1})$ by the Auslander-Reiten formula. This induces isomorphisms
\begin{align}
  \label{eq:homext} 
  \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}. \tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).
\end{align}
This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between the basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$. 
In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_m^{[k]}$. Finally note that there exists a short exact sequence
\[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
\end{enumerate}
\end{remark}

@@

\begin{tikzpicture}[scale=1.35]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

For $m\geq 3$, the truncated preprojective $\tau\tilde P_{m+1}^{[k]}\cong\tilde P_{m-1}^{[k]}$ can uniquely be found as a quotient of $\tilde P_{m,k}$. This can also be seen on the level of $2$-quivers, i.e. we find $\cQ_{m-1}^{[k]}$ as a subquiver of $\cQ_{m,k}$.  More precisely, this subquiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,k}$.  Now the $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$ of $\tilde P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ to $\mathcal Q_{m,k}$ by a $2$-arrow. Thereby, the $2$-arrow connects $\mathcal Q_{m+1}^{[k]}$ to the subquiver $\cQ_{m-1}^{[k]}$ in $\cQ_{m,k}$. This gives the following $2$-quiver $\mathcal Q_{m+1}^{[k-1]}$:
\\
\begin{flushleft}
\begin{tikzpicture}[scale=0.97]
\draw (0,4) node (A1) {\footnotesize$\mathcal Q_{m-1,1}$}+(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,k}$} +(1.6,0) node (B1) {\footnotesize$\mathcal Q_{m-1,2}$}+(1.6,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$} +(3.2,0) node (B11) {\footnotesize$\dots$} +(4.6,0) node (D1) {\footnotesize$\mathcal Q_{m-1,n-1}$}  +(6.4,0) node (E1) {\footnotesize$\mathcal Q_{m-2,2}$} +(4.8,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}+(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}+(8.0,0) node (A1b) {\footnotesize$\dots$} +(9.6,0) node (B1b) {\footnotesize$\mathcal Q_{m-2,k+1}$}+(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[k]}$} +(11.2,0) node (B11b) {\footnotesize$\dots$} +(12.8,0) node (D1b) {\footnotesize$\mathcal Q_{m-2,n-1}$} +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$} +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$} ; 
\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
\draw[<-,red] (D1b)--(E1b) node[pos=.5,above] {};
\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {};
\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {};
\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {};
\draw[->,red] (Q41)--(E1) node[pos=.5,above] {};
\draw[->,red] (Q51)--(D1) node[pos=.5,above] {};
\draw[->,red] (Q61)--(B11) node[pos=.5,above] {};
\draw[->,red] (Q71)--(B1) node[pos=.5,above] {};
\draw[->,red] (Q81)--(A1) node[pos=.5,above] {};

@@

\node (PMK) [draw=black,fit={(Q2b) (B)}]{};
\draw[->,red,thick] (PMK)--(Q31);
\end{tikzpicture}
\\
\end{flushleft}
\noindent 
%In order to keep the diagrams as simple as possible we did not insert the labels of the vertices. As every vertex  $q\in(\mathcal Q_m^{[k]})_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$, in any case it is straightforward to associate an arrow $\alpha_i\in K(n)_1$ with every ($2$-)arrow of $\mathcal Q_m^{[k]}$. 
 As already mentioned two different vertices of $\mathcal Q_m^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$. Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[k]})_0$ are defined by
$$\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G_{K(n)}\tbfe (\beta)\in\NN^{K(n)_0}$$
where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta\subset (\mathcal Q_m^{[k]})_0$.

@@

The following result is an immediate consequence of the combinatorial construction of rank 2 cluster variables \cite{llz} and the categorification of these variables using representations of $K(n)$ \cite{cc,ck}.
\begin{theorem}\cite{llz}
  For each $m\ge1$ and $\bfe\in\ZZ_{\ge0}^2$, we have $\chi\big(\Gr_\bfe(P_m)\big)=\big|\{(S_H,S_V)\in\cC_m:|S_H|=u_m-e_1,|S_V|=e_2\}\big|$.
\end{theorem}

Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(\Gr^Q_\bfe(P_m)\big)$ found in Theorem~ ?%\ref{???}.
